Music Versus No Music Effectiveness On Cognitive Response Time and Typing Efficiency

### 2024-05-04 Latex Source/paper.tex
fix images

\subsection[short]{Design}
After obtaining consent from all participants, they proceeded to take the typing test. The test presented lyrics from popular songs within a graphical user interface (GUI). 
The interface automatically calculated typing accuracy and the time the attempt took in the program's backend, allowing participants to focus solely on completing the test.
Each participant completed the typing test under three conditions: music with lyrics, music without lyrics, and no music (silent condition).
Multiple levels of music intensity were utilized within each condition to assess varying degrees of distraction.
The GUI of the typing test was built with simplicity in mind. The starting window was pulled up so as not to confuse participants with the code as seen in Figure 1. The participants saw Figure 2 while the test is running, while Figure 3 is the signifier that the typing portion is finished.

@@

During the cognitive task component of the study, participants performed a Quantified Behavioral test or QBTest while their eye movements were tracked by the EyeWriter 2.0.
The QBTest is a computerized test designed to assess various aspects of cognitive function, including attention, impulsivity, and response control.

>>>>

\subsection[short]{Design}
After obtaining consent from all participants, they proceeded to take the typing test. The test presented lyrics from popular songs within a graphical user interface (GUI). 
The interface automatically calculated typing accuracy and the time the attempt took in the program's backend, allowing participants to focus solely on completing the test.
Each participant completed the typing test under three conditions: music with lyrics, music without lyrics, and no music (silent condition).
Multiple levels of music intensity were utilized within each condition to assess varying degrees of distraction.
The GUI of the typing test was built with simplicity in mind. The starting window was pulled up so as not to confuse participants with the code as seen in Figure 1a. The participants saw Figure 1b while the test is running, while Figure 1c is the signifier that the typing portion is finished.

@@

During the cognitive task component of the study, participants performed a Quantified Behavioral test or QBTest while their eye movements were tracked by the EyeWriter 2.0.
The QBTest is a computerized test designed to assess various aspects of cognitive function, including attention, impulsivity, and response control.
% MAYBE ADD MORE ABOUT THE QBTEST?
